Response to Reviewer 2

### 2015-08-24 response2.tex
com comentarios do Danilo para respostas ao referee

\vspace{2mm}
{\bf Response: the referee is correct in point out that our previous analyses did not include formal paired hypotheses tests concerning the performance of the models. We have now included pairwise comparisons (both statistical tests and graphical analyses), and changed the text accordingly; the new material is highlighted in dark green. Please let us know whether the new version is more sound.

>>>>

\vspace{2mm}
{\bf Response: the referee is correct in point out that our previous analyses did not include formal paired hypotheses tests concerning the performance of the models. We have now included pairwise comparisons (both statistical tests and graphical analyses). We have decided to perform Friedman's rank sum test during the analysis, since Friedman test is an analog of the approaches suggested in the reviewer's comments, and it also allows us to make multiple comparisons among models.  The text was modified accordingly; the new material is highlighted in dark green. Please let us know whether the new version is more sound.
